### 2012-11-22 inst/examples/mult_uncertainty_test.Rmd
numerical instabilities in uniform noise case?

@@

```{r}
#' SDP under multiple uncertainty
#'
#' Computes the SDP solution under the case of growth noise, 
#' implementation errors in harvesting, and meaurement errors in 
#' the stock assessment.  
#'
#' @param f the growth function of the escapement population (x-h)
#'   should be a function of f(t, y, p), with parameters p
#' @param p the parameters of the growth function
#' @param x_grid the discrete values allowed for the population size, x
#' @param h_grid the discrete values of harvest levels to optimize over
#' @param sigma is the shape parameters for noise distribution (sigma_g, sigma_m, sigma_i) (default is no noise)
#' @param pdfn is the probability density function (same functional form is used for growth, measure, implement).  (Default is uniform)
#' @param profit is the profit function (defaults to the realized harvest)
#' @return The D matrix giving the optimal harvest for each possible state in each timestep.  
#' Hence the optimal policy at time t is given by the policy function D[,t].  
#' Values of D[,t] correspond to the index of h_grid.  Indices of of D[,t] correspond to states in y_grid.  
#' @export
SDP_multiple_uncertainty <- function(f, p, x_grid, h_grid, Tmax = 25,
                                     sigmas =c(sigma_g=0, sigma_m=0, sigma_i=0), 
                                     pdfn = pdfn, profit = function(x,h) pmin(x, h)){

@@

    # integrate over uncertainty in I and X 
    F <- lapply(1:n_h, function(q){  
      t(sapply(1:n_x, function(y){
        out <- numeric(n_x)
        mu <- sum(sapply(1:n_x, function(x)
          f(x_grid[x],h_grid,p) %*% I[q,] *  M[y,x])) # Implementation & Measurement error
        if(mu==0)
          out[1] <- 1   
        else 
          out <- dlnorm(x_grid/mu, 0, sigma_g)
        out/sum(out)
      }))
    })

@@

pars <- c(1.5, 0.05)
K <- (pars[1] - 1)/pars[2]
xmin <- 0
xmax <- 1.5 * K
n_x <- 120
n_h <- n_x
x_grid <- seq(xmin, xmax, length = n_x)  
h_grid <- seq(xmin, xmax, length = n_h)
delta <- 0.05
xT <- 0
OptTime <- 25
sigma_g <- 0.5
````

>>>>

```{r plotting, include=FALSE}
theme_publish <- theme_set(theme_bw(14))
theme_publish <- theme_update(
        # panel.grid.major=element_blank(), panel.grid.minor=element_blank(),
        legend.title=element_blank(), 
        panel.background = element_rect(fill = "transparent",colour = NA), 
        plot.background = element_rect(fill = "transparent",colour = NA))
```

@@

```{r}
#' SDP under multiple uncertainty
#'
#' Computes the SDP solution under the case of growth noise, 
#' implementation errors in harvesting, and meaurement errors in 
#' the stock assessment.  
#'
#' @param f the growth function of the escapement population (x-h)
#'   should be a function of f(t, y, p), with parameters p
#' @param p the parameters of the growth function
#' @param x_grid the discrete values allowed for the population size, x
#' @param h_grid the discrete values of harvest levels to optimize over
#' @param sigma is the shape parameters for noise distribution (sigma_g, sigma_m, sigma_i) (default is no noise)
#' @param pdfn is the probability density function (same functional form is used for growth, measure, implement).  (Default is uniform)
#' @param profit is the profit function (defaults to the realized harvest)
#' @return The D matrix giving the optimal harvest for each possible state in each timestep.  
#' Hence the optimal policy at time t is given by the policy function D[,t].  
#' Values of D[,t] correspond to the index of h_grid.  Indices of of D[,t] correspond to states in y_grid.  
#' @export
SDP_multiple_uncertainty <- function(f, p, x_grid, h_grid, Tmax = 25,
                                     sigmas =c(sigma_g=0.3, sigma_m=0, sigma_i=0), 
                                     pdfn = pdfn, profit = function(x,h) pmin(x, h)){

@@

    # integrate over uncertainty in I and X 
    F <- lapply(1:n_h, function(q){  
      t(sapply(1:n_x, function(y){
        out <- numeric(n_x)
        mu <- sum(sapply(1:n_x, function(x)
          f(x_grid[x],h_grid,p) %*% I[q,] *  M[y,x])) # Implementation & Measurement error
        if(mu==0)
          out[1] <- 1   
        else {
         out <- pdfn(x_grid, mu, sigma_g)
         if(sum(out) == 0)
           out[1] = 1
         out
        }
        out/sum(out)
      }))
    })

@@

pars <- c(1.5, 0.05)
K <- (pars[1] - 1)/pars[2]
xmin <- 0
xmax <- 1.5 * K
n_x <- 200
n_h <- n_x
x_grid <- seq(xmin, xmax, length = n_x)  
h_grid <- seq(xmin, xmax, length = n_h)
delta <- 0.05
xT <- 0
OptTime <- 25
sigma_g <- 0.5
````
